---
title: The Avengers
author:
- Thor (UNIST)
- Iron Man (Hanyang University)
documentclass: article
output:
  pdf_document:
    keep_tex: yes
  html_document:
    df_print: paged
  github_document:
  html: null
nocite: |
  <!-- bae2014invariance -->
fontsize: 12pt
params:
  format: "latex"
bibliography: references.bib
abstract: |
  This paper examines ...
---

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
      font-family: "Times New Roman", Times, serif;
  }
td {  /* Table  */
  font-size: 20px;
}
h1.title {
  font-size: 24px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 22px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 22px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 20px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 20px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(dplyr)
library(tibble)
library("knitr")
```


\setlength{\parindent}{1cm}

# Introduction

@bae2014invariance investigate ... 123

# Literature Review

We review the literature ... 

# Data and Methods

The methods of event study separate ...

## Data

Subsection

## Methods

Subsection

\begin{center}
<Insert Table 1>
\end{center}

# Results 

We examine the relationship between ...

$$ r_{t \rightarrow t+k}= \beta_0 + \beta_1 \cdot x_t +\varepsilon_{t \rightarrow k} $$

# Conclusion

We identify the relations between ...

\newpage

# Tables and Figures


```{r, results='asis',echo=FALSE, message=FALSE, warning=FALSE, comment=FALSE}
stargazer(attitude,type=params$format,header=FALSE)
```

\newpage

```{r, fig.cap="A caption",echo=FALSE, message=FALSE, warning=FALSE, comment=FALSE}
plot(attitude$rating,attitude$complaints,main="test")
```

\newpage

# References
